\begin{abstract}
Interdisciplinary  analyses are prone to misunderstandings associated with rich
discipline-specific semantics. The research of low carbon energy systems is an
example of such applications where concepts coming from multiple expert groups
collide. One relevant case is the transport-energy nexus where `sector-coupling'
analyses are performed. In this context battery electric vehicle charging
infrastructure comprises a main point of interaction for both research
disciplines. Ontologies like the Open Energy Ontology (OEO) where conceived to
aid in the concretization of agreement in such interdisciplinary research. But
since it is a tool whose focus is  energy systems research, it falls short in
concepts associated with transportation research. In this paper we propose a
FAIR Ontology, which should work as a first interoperability layer between
ontologies and data models intending to represent concepts associated with
battery electric vehicle charging infrastructure.  We rely on the Basic Formal
Ontology (BFO) as top-level ontology, to ensure compatibility with OEO. We
develop this ontology using a methodology inspired by the OEO with a stricter
requirements engineering approach. This methodology relies strongly on
motivating scenarios and competency questions to keep the ontology slim. Current
achievements are a documented development environment, the implementation of
core terms like charging station and  reutilization of existing ontology terms
coming from ontologies like the OEO, the Common Core Ontologies and the iCity
Transport Planning Suite of Ontologies.
\end{abstract}