\section{Development status and future roadmap}
\label{achievment}

At the time of this publication the ontology has an open git
repository\footnote{Note for the editors: The publishing of the repository is
being subject to export control, we would update the links accordingly in the
camera ready version. }. This repository has a documentation where the
motivating scenarios along their competency questions are written. A quick
introduction for developers is also part of this documentation. Infrastructure
for automatic evaluation of competency questions as well as consistency checks
are implemented. We also import the entire CCO version of the BFO which already
includes basic RO axioms. We import  the excerpts from OEO and CCO to be
reutilized using scripts to increase transparency and reproducibility. These
steps point to specific versions of the ontologies that can be updated based on
developing needs. 

The next milestone is to have implemented the terminology associated with the
first two scenarios. Followed by a demonstration application based on scenario
one using the FAIR version of the German network agency data that we extracted
for \cite{ArellanoRuiz.2024}.

One important open issue is hosting of the ontology. Currently, we use the
namespace of the Open Energy Platform, but we are not sure if they would
consider it part of the scope of their project. One alternative could be
upcoming repository of ontologies often mentioned in the discussion board of
the CCO. At the time of writing this paper we propose having this discussion
during the workshops of these proceedings.