\section{Background}
\label{statementofneed}
The need of an ontology that represents entities and phenomena associated with
charging infrastructure was identified first during the process of implementing
the FAIR principles on the data published by the German Network Agency
\cite{ArellanoRuiz.2024}. There we noticed that the existing ontologies and
vocabularies where insufficient to annotate concepts like charging plug type.
After a short discussion in the OEO issue
board\footnote{https://github.com/OpenEnergyPlatform/ontology/issues/1597} we
came to the conclusion that thing like `power plug' and potential subclasses of
the same are beyond the scope of the ontology. Along concepts like `parking
place' or `mobility mode', which are often used during transportation research
analyses, it has been hard to argue to include them in the OEO, despite them
being used during cross-domain analyses like the one done by \cite{Hecht.2022}.
This need is deeply explored by \cite{Mittermeier.2023}, but their approach
used to address it relied mostly on including the terms in the OEO which we
consider not viable in the long run. However, their research provides a solid
theoretical basis to further developments in the field of knowledge
representation of terminology in the discipline of transport research.

Katsumi and Fox \cite{Katsumi.2018} provide an extensive review of transport
ontologies, taxonomies, vocabularies and other tools for data representing
information of transport systems. They shed light on the large complexity of
the data environments associated to this discipline. Their research concretized
in the creation of the iCity Transportation Planning Suite of Ontologies (TPSO)
\cite{Katsumi.2019}. We will be referencing their work in further sections.
They touch on the topic of charging infrastructure on a superficial level which
is sufficient for transportation planning tasks. What we propose in this work
is an extension that promises interoperability with planning grid
infrastructure and energy consumption estimations. The particular applications
are explored in section \ref{methodology} where we define scenarios that drive
and bound the ontology development. It is important to point out that the
actual implementations differ significantly from the TPSO because they define
their own top-level ontology which is fundamentally different from BFO, the
particularities of these differences are described in section \ref{upperlevel}.

There are some other vocabularies and models that deal with charging
infrastructure, but most of them are constrained by their specific
applications, as they prescribe what would be expected from the data models
produced out of them. One important mention is the work from
\cite{MaximeLefrancois.2017} who proposed a power-systems ontology aimed at
interoperability of the IoT domain. They provide a rich axiomatization of
charging infrastructure that is strongly skewed towards power systems'
representation. Some elements of interest to us are present, but most relations
are specific to IoT. Relations with entities external to an IoT network like
vehicles are not considered and adding them to the imported ontology would
render it inconsistent given its rigid range and domain constraints. 