\section{Discussion}
\label{discussion}

One of the main disadvantages of writing competency questions as queries for
most concepts is that implementations are slow. We consider that the benefits
outweigh the drawbacks as the outputs are ensured to be concise without much
further validation, as the validation occurs during the question definition
(think Test Driven Development \cite{ArellanoRuiz.2022}). Sometimes is
challenging to come up with competency questions when there are no
implementations to refer to. The CCO provides clear documentation that we can
turn to in such cases. Another problem is that the actual software implementation
relies on calling java as a subprocess from Python. The alternative would have
been to use Clojure. But we are optimistic that thanks to new OWL-aware
tools like horned-owl and its respective python embedding
py-horned-owl\footnote{https://github.com/phillord/horned-owl,
https://github.com/jannahastings/py-horned-owl} we will eventually be able to
migrate to a pure python solution. The only issue stopping us from using them
directly is that they have yet to support some DL reasoner.

The next milestone is to complete the terminology associated with the first two
scenarios. As well as designing two further scenarios, each associated with a
service. The first consists of a day-ahead stochastic forecasting application
for single and groups of stations. The second is for the aggregated
estimation of bidirectional charging potentials and charging flexibility
calculated by the tool {venco.py} \cite{Miorelli.2024}.  
We intend to do practical demonstrations  by adjusting data models based on
scenario one using the FAIR version of the German network agency data that we
extracted for \cite{ArellanoRuiz.2024}.

One important open issue is the hosting of the ontology. Currently, we use the
namespace of the Open Energy Platform, but we are not sure if they would
consider it part of the scope of their project. One alternative could be an
upcoming repository of ontologies often mentioned in the discussion board of the
CCO. Our last alternative is to prepare some form of self-hosting. At the time
of writing this paper, we propose having this discussion during the workshops of
these proceedings.
